### 2012-07-28 inst/examples/managed_warning.Rmd
running on zero
debug on managed warning

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="criticaltransition/" or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 200
sigma_g <- .5
````

@@

``` {r noise}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r earlywarning}
acor_tau <- dt[fishstock > 1.5, 
               warningtrend(data.frame(time=time, value=fishstock),
                            window_autocorr),
               by=reps]

var_tau <- dt[fishstock > 1.5, 
              warningtrend(data.frame(time=time, value=fishstock),
                          window_var),
              by=reps]
````

``` {r modelbased}
m <- dt[fishstock > 1.5, 
        stability_model(data.frame(time=time, value=fishstock),
                          "LSN")$pars["m"],
        by=reps]
````

@@

``` {r earlywarning2}
acor_tau <- dt[unharvested > 1.5, 
               warningtrend(data.frame(time=time, value=unharvested),
                            window_autocorr),
               by=reps]

var_tau <- dt[unharvested > 1.5, 
              warningtrend(data.frame(time=time, value=unharvested),
                          window_var),
              by=reps]
````

``` {r modelbased2}
m <- dt[unharvested > 1.5, 
        stability_model(data.frame(time=time, value=unharvested),
                          "LSN")$pars["m"],
        by=reps]
````

>>>>

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 200
sigma_g <- .1
````

@@

``` {r noise}
z_g <- function() dlnorm(1, 0, sigma_g)
````

@@

``` {r earlywarning}
acor_tau <- dt[, 
               warningtrend(data.frame(time=time, value=fishstock),
                            window_autocorr),
               by=reps]

var_tau <- dt[, 
              warningtrend(data.frame(time=time, value=fishstock),
                          window_var),
              by=reps]
````

``` {r modelbased}
m <- dt[, 
        stability_model(data.frame(time=time, value=fishstock),
                          "LSN")$pars["m"],
        by=reps]
````

@@

``` {r earlywarning2}
acor_tau <- dt[, 
               warningtrend(data.frame(time=time, value=unharvested),
                            window_autocorr),
               by=reps]

var_tau <- dt[, 
              warningtrend(data.frame(time=time, value=unharvested),
                          window_var),
              by=reps]
````

``` {r modelbased2}
m <- dt[, 
        stability_model(data.frame(time=time, value=unharvested),
                          "LSN")$pars["m"],
        by=reps]
````
